Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2021-06-24 theory.tex
Corrected feed typo.
Co-authored-by: Katie Mummah <radioactivekate@gmail.com>
expanding on first principles derivation

It can be shown \cite{avery} that the separative power of a single centrifuge can be
derived from first principles and expressed as a function of the feed-to-product enrichment factor, $\alpha$, the cut, $\theta$, and the feed rate, $F$:
%I think we should replicate at least some of that here

\begin{equation} \label{eq_alpha_principle}
    \delta U = \frac{F}{2}\frac{\theta}{1-\theta}(\alpha-1)^{2}
\end{equation}

@@

\begin{equation}
    F_{i} = T_{i+1} + F_{i-1} ~(+ F_{ext})
\end{equation}

>>>>

Separative power can be written as a function of the change in entropy performed \cite{avery}:

\begin{equation}
    \delta U = \frac{L}{RN} \frac{\Delta S}{(1-N)}
\end{equation}

Here, $L$ is the feed flow expressed as moles per second and could be interchangeably expressed as $F$ above.
Using the Boltzmann definition of entropy, the change in entropy for a mixture of two isotopes is:

\begin{equation}
    \Delta S(N) = R \left( N \ln(N) + (1-N) \ln(1-N) \right)
\end{equation}

Using this in the expression for free energy \cite{?} and normalizing for temperature and gas constant,
a value function can be constructed \cite{?}:

\begin{equation}
    V(x) = (2x-1) \ln{(\frac{x}{1-x})}
\end{equation}

Where $x$ here is a concentration for a mass (e.g. $N$). The separative work applied on a feed is then an expression of this value function:

\begin{equation}
    \delta U = \theta F V(N') + (1-\theta) F V(N'') - F V(N)
\end{equation}

Conducting a Taylor expansion of $V(N)$ around $N$ and utilizing the definition $N=\theta N' + (1-\theta)N''$ lends a simplification:

\begin{equation}
    \delta U = \frac{\theta}{1-\theta} \frac{F(\alpha-1)^2}{2} \frac{d^2 V(N)}{dN^2} \left[ N(1-N) \right]^2
\end{equation}

Finally, specifying the change in value function to be independent of $N$ (?) concludes in an expression for the separative power of a single centrifuge
in terms of the feed-to-product enrichment factor, $\alpha$, the cut, $\theta$, and the feed rate, $F$ \cite{avery}:
%I think we should replicate at least some of that here

\begin{equation} \label{eq_alpha_principle}
    \delta U = \frac{\theta}{1-\theta}\frac{F}{2}(\alpha-1)^{2}
\end{equation}

@@

\begin{equation}
    F_{i} = T_{i+1} + P_{i-1} ~(+ F_{ext})
\end{equation}
